---
title: 'HW 11: Function plotting and randomization tests'
author: "Alex Neidermeier"
date: "4/4/2018"
output: 
  prettydoc::html_pretty:
    theme: "cayman"
    highlight: github
---
#Problem 1:
* Calculating Growing Degree Days for *Leucopis* spp. 

```{r}
library(ggplot2)
library(fitdistrplus)
######################################################
# FUNCTION: HLT  ---------------------------------------------------
# Generates random high and low temps for a specified number of days
# input:  n = number of days 
#         
# output: S = vector of species richness
#----------------------------------------------------
HLT <- function(n=7*9, meantemp=15){
  HTemps <- data.frame(HTemps=rnorm(n=n,mean=meantemp+5,sd=2.5))
  LTemps <- data.frame(LTemps=rnorm(n=n,mean=meantemp-5,sd=1.5))
  TempsDF <- data.frame(Htemps=HTemps,Ltemps=LTemps)
  return(TempsDF)
}
# t <- HLT()

######################################################
# FUNCTION: GDD ---------------------------------------------------
# Determines growing degrees days for silver fly spp
# input:  DMax  =   Daily Maximum Temperatures
#         DMin  =   Daily Minimum Temperatures 
#         BLine =   Baseline temperature
# output:   DD  =   Degree day value
#----------------------------------------------------
GDD <- function(DMax=18,
                DMin=10,
                BLine=11){
  DD <- ((DMax+DMin)/2)-BLine
  return(DD)
}
# GDD()

#FUNCTION: LPSF5. LPSF= Leucopis Population Simulation Function
#Produces a vector of simulated leucopis Populations from accumulated degree days
#input: x = accumulated growing degree days 
#output: Estimate of Leucopis pops 
#_________________________________________________________
LPSF5 <-function(x=df$V4){ 
  noise <- runif(length(x),-20,20)
  y=10+2*x+noise # y= resulting leucopis pop
  return(y)
}
#y <- LPSF5()


#FUNCTION: LPSF6. LPSF= Leucopis Population Simulation Function
#Produces a vector of simulated leucopis Populations from accumulated degree days
#Runs a linear model
#Creates a ggplot with a smoother
#Returns the plot, slope, and p-values
#input: x = accumulated growing degree days 
#output: Plot w/ smoother (+axis names), print slope & p-value
#_________________________________________________________
LPSF6 <-function(x,y){ 
  Exp2 <- data.frame(x,y)
  myMod <- lm(y~x) #fits model
  myOut <- c(slope=summary(myMod)$coefficients[2,1],pval=summary(myMod)$coefficients[2,4])
  plotVar <- ggplot(data = Exp2, aes(x=x,y=y))+ geom_point()+ stat_smooth(method = lm, se=0.99)
  print(plotVar)
  return(myOut)
}

#FUNCTION: LPSF_NP. LPSF= Leucopis Population Simulation Function
#Produces a vector of simulated leucopis Populations from accumulated degree days
#Runs a linear model
#Creates a ggplot with a smoother
#Returns the plot, slope, and p-values
#input: x = accumulated growing degree days 
#output: Plot w/ smoother (+axis names), print slope & p-value
#_________________________________________________________
LPSF_NP <-function(x,y){ 
  Exp2 <- data.frame(x,y)
  myMod <- lm(y~x) #fits model
  myOut <- c(slope=summary(myMod)$coefficients[2,1])
  return(myOut)
}


######################################################
# FUNCTION: shuffleData
# randomize data for regression analysis
# input: Data frame elements, xVar, yVar. SC=shuffle column
# output: data frame (ID, xVar, yVar) w/ one column shuffled
#-----------------------------------------------------

shuffleData <- function(z){
  z <- sample(z)
  return(z)
}
#shuffleData()

```

```{r}
######################################################
# FUNCTION: getPVal
# calculate p value for observed, simulated data
# input: list of observed metric and vector of simulated metric (list needs to be in same form all the time)
# output: lower, upper tail probability vector
#-----------------------------------------------------

getPVal <- function(z=NULL){
  if(is.null(z)){
  z <- list(Xobs=runif(1),Xsim=runif(1000))}
  pLower <- mean(z[[2]]<=z[[1]])#have to use dbl bracks for a list
  pUpper <- mean(z[[2]]>=z[[1]])
  return(c(pL=pLower,pU=pUpper))
}

######################################################
# FUNCTION: plotRanTest
# calculate p value for observed, simulated data
# input: list of observed metric and vector of simulated metric (list needs to be in same form all the time)
# output: lower, upper tail probability vector
#-----------------------------------------------------
plotRanTest <- function(z=NULL){
  if(is.null(z)){ 
    z <- list(xObs=runif(1),xSim=runif(1000))}
  dF <- data.frame(ID=seq_along(z[[2]]), simX=z[[2]])
  p1 <- ggplot(data = dF,mapping=aes(x=simX))
  p1+ geom_histogram(mapping=aes(fill=I("goldenrod"),color=I("black")))+geom_vline(aes(xintercept=z[[1]],col="blue"))
}

```


### Main Body of Code
* Get degree days. df has my high & low temps
```{r}
df <- HLT()
# Loop to run GDD function over degree data to get daily increase in degree days
for(i in 1:nrow(df)){
  for(j in 2:nrow(df)){
  df[i,3] <- GDD(DMax = df[i,1],DMin = df[i,2])
  df[1,4] <- df[1,3]
  df[j,4] <- df[(j-1),4]+df[j,3] 
  df[i,5] <- LPSF5(x=df[i,4])
  }
}

```

* Plot degree days vs leucopis pops.
```{r}
# Feed that into a function that produces a ggplot and gives me the slope and pval
Xobs <- LPSF6(df$V4,df$V5)

```


##Problem 2: Randomization test using shuffling function
```{r}
df2 <- HLT()
# Loop 1
for(i in 1:nrow(df)){
  for(j in 2:nrow(df)){
  df[i,3] <- GDD(DMax = df[i,1],DMin = df[i,2])
  df[1,4] <- df[1,3]
  df[j,4] <- df[(j-1),4]+df[j,3] 
  df[i,5] <- LPSF5(x=df[i,4])
  }
}

# Shuffle test
S <- data.frame(GDD=df$V4,Pop=shuffleData(df$V5))

# Plot,slope, pval of shuffled data
LPSF6(df$V4,df$V5)

```

* Do 1000 shuffles
```{r}
nsim=1000
Xsim <- vector(length = nsim) # will hold simulated slopes

for(i in seq_len(nsim)){
  Xsim[i] <- LPSF_NP(df$V4,shuffleData(df$V5))
}

head(Xsim)

slopes <- list(Xobs[1], Xsim)
getPVal(slopes)

plotRanTest(slopes)

```

This was a challenging excercise for me to understand conceptually and also to execute (I took two full class periods and then some!).  I'm still not totally clear on why pL and pU from the getPVal function were 1 and 0 respectively--my thought is that my data simulation is probably too tight (ie not enough noise) so it is way to the right of the other simulated slopes.  I think it might make more sense to do this for the pvalues than with the slope.

