---
title: 'HW 12: ggplot time!'
author: "Alex Neidermeier"
date: "4/11/2018"
output: 
  prettydoc::html_pretty:
    theme: "cayman"
    highlight: github
---
#Function plotting and randomization tests#
* Make my life cycle analysis bar graph in R
* Then do facets of each part of life cycle over four weeks

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning=FALSE)
```


```{r}
library(ggplot2)
library(ggthemes)
library(patchwork)
library(tidyr)
library(wesanderson)
```

## Initial Tinkering--incorrect data format
```{r}
z <- read.table("FY17LeucopisPops.csv",header=TRUE,sep=",", stringsAsFactors=FALSE)
str(z)
fl <- z[,2:5]
str(fl)

#At least have the dates on the x axis here
p1 <- ggplot(data = z,mapping = aes(x=z$Dates))+ geom_bar(color="black", fill="goldenrod")
print(p1)

#trying to use geom_col instead
# At least get the larvae plotted correctly here!
p1 <- ggplot(data=z,aes(x=Dates))+geom_col(aes(y=Larvae))
print(p1)

```

Using the gather function to wrangle my data
```{r}
colnames(z)=c("Dates","Parent generation","Larvae","Pupae","F1 Generation")
. <- gather(z,"Parent generation":"F1 Generation",key = Life_Stage, value = "Abundance")
print(.)

.$Abundance <- as.numeric(.$Abundance)
LeuLong <- .

# This works but need to change themes, reorganize legend and title, etc.
LeuData2 <- LeuLong[order(LeuLong$Dates),]
LeuBar2 <- ggplot(LeuData2,aes(x=Dates, y=Abundance,fill=Life_Stage, legend(title = "Life Stage")))+
  geom_bar(position="dodge",stat="identity",color="black")
LeuBar2

# Different themes
  LeuBar2 <- LeuBar2+theme_linedraw()
LeuBar2

# Flipped axes
LeuBar2 + coord_flip() + theme_grey(base_size = 20, base_family = "Courier")

# With title and fixed axes
LeuBar2 <- LeuBar2 + ggtitle("Leucopis spp. abundance", subtitle = "New York 2017") +xlab("Collection Dates")+ylab("Leucopis Abundance by life stage")+theme_classic()
LeuBar2

```


##Try making individual graphs and then stacking them \

```{r}
# Using patchwork to have panels of each life stage 
p0 <- ggplot(data=z,aes(x=Dates))+geom_col(aes(y=z$"Parent generation"),fill="black")+ ggtitle("Parent Generation") +xlab("Collection Dates")+ylab("Adult Abundance")+theme_linedraw()
print(p0)

p1 <- ggplot(data=z,aes(x=Dates))+geom_col(aes(y=Larvae),fill="pink")+ggtitle("Larvae Abundance") +xlab("Collection Dates")+ylab("Larvae Abundance")+theme_linedraw()
print(p1)

p2 <- ggplot(data=z,aes(x=Dates))+geom_col(aes(y=Pupae),fill="green") +
  ggtitle("Larvae Abundance")+ xlab("Collection Dates")+ylab("Pupae Abundance")+theme_linedraw()
print(p2)

p3 <- ggplot(data=z,aes(x=Dates))+geom_col(aes(y=z$"F1 Generation"),fill="purple") + 
  ggtitle("F1 Abundance")+ xlab("Collection Dates")+ylab("F1 Abundance")+theme_linedraw()
print(p3)


#Using Patchwork to place them vertically and horizontally
p0+p1+p2+p3+plot_layout(nrow=1)

p0+p1+p2+p3+plot_layout(ncol=1)

# And then in two rows 
(p0 | p1 )/(p2 |p3)

```
*This looks a little crowded with all the axes

##Trying using a different color palette 
*Improve legend and colors on this graph.\
```{r}
LeuBar2 <- ggplot(LeuData2,aes(x=Dates, y=Abundance,fill=Life_Stage))+geom_bar(position="dodge",stat="identity",color="black")+theme_classic()
LeuBar2

# Get rid of legend title
LeuBar2 <- ggplot(LeuData2,aes(x=Dates, y=Abundance,fill=Life_Stage))+ geom_bar(position="dodge",stat="identity",color="black")+guides(fill=guide_legend(title=NULL))+theme_classic()
LeuBar2

#Trying to fix the legend order. Got it!!
LeuBar2 <- LeuBar2 + scale_fill_discrete(breaks=c("Parent generation","Larvae","Pupae","F1 Generation"))

LeuBar3 <- LeuBar2+scale_fill_manual(values = wes_palette("GrandBudapest2"))
LeuBar3

LeuBarDar <- LeuBar3+scale_fill_manual(values = wes_palette("BottleRocket2"))
LeuBarDar
?wes_palettes

LeuBarDar <- LeuBar3+scale_fill_manual(values = wes_palette("BottleRocket2"),breaks=c("Parent generation","Larvae","Pupae","F1 Generation"))
LeuBarDar

# Fixing up the plot format
LeuBarDar <- LeuBarDar+ ggtitle("Leucopis spp. abundance", subtitle = "New York 2017") +xlab("Collection Dates")+ylab("Leucopis Abundance by life stage")+theme_bw()
LeuBarDar 


```

More faceting!
```{r}
LeuBarDar+facet_grid(.~Dates)
LeuBarDar+facet_grid(.~Dates,scales = "free", switch = "x")

LeugraphWSJ <- LeuBarDar+facet_wrap(~Dates,ncol = 1)+theme_wsj()
LeugraphWSJ

Leugraphbw <- LeuBarDar+facet_wrap(~Dates,ncol = 1)+theme_bw()+
  theme(axis.title.x=element_blank(),
        axis.text.x=element_blank(),
        axis.ticks.x=element_blank())
Leugraphbw

```

