---
title: "HW 6: Creating Fake Data Sets To Explore Hypotheses"
author: "Alex Neidermeier"
date: "2/28/2018"
output: 
  prettydoc::html_pretty:
    theme: "cayman"
    highlight: github
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(reshape2)
```

##Simulated Leucopis Data##

###Take 1###
*Creating a results matrix
```{r}
resultsMatrix <- matrix(NA,1,1)
colnames(resultsMatrix) <- list("P value")
#print(resultsMatrix)

```

*Experiment 1:*
Counting the number of leucopis flies and temperature which are both continuous variables

* Hypothesis: The insect population will come to a peak and then fall

* 2. Analysis type: Regression

* 3. Data simulation:
```{r}
#LPSF= Leucopis Population Simulation Function
#Produces a table of rnorm Temperatures and Populations
LPSF1 <- function(TempMean=10,PopsMean=20,n=50,sd1=1,sd2=3){
  Exp1 <- data.frame(Temps=rnorm(mean=TempMean,n=n,sd=sd1),Pops=rnorm(mean=PopsMean,n=n,sd=sd2))
  return(Exp1)
}  
#Exp1 is my first sample set
Exp1 <- LPSF1(TempMean = 15)
head(Exp1)


```

* 4. Function:
```{r}
#LMA means linear model analysis
#Sample size: 
LMA1 <- function(data=Exp1){
  Results1 <- lm(Temps~Pops,data = data)
  return(summary(Results1)$coefficients)
}
z1 <- LMA1()
#This gives you just the p-value.  Need to find a way to get this into my results matrix w/ 
z1[2,4] <- resultsMatrix
```

* 4. Plot:
```{r}
#This is a function to plot the results of my linear model
RegPlotF <- function(data=Exp1){
  Exp1Plot <- ggplot(data = data, aes(x=Temps,y=Pops))+ geom_point()+ stat_smooth(method = lm, se=0.99)
  print(Exp1Plot)
}
RegPlotF()

```

5. Rerunning three times:
*1. 
```{r}
Exp1 <- LPSF1()
z <- LMA1()
z[2,4]
RegPlotF()

```
2. 
```{r}
Exp1 <- LPSF1()
z2 <- LMA1()
resultsMatrix <- rbind(z2[2,4])
RegPlotF()

```
3.
```{r}
Exp1 <- LPSF1()
z3 <- LMA1()
resultsMatrix <- rbind(z3[2,4])
RegPlotF()

```

#####6. Adjusting means of groups#####
* Changing the temperature mean
```{r}
Exp1 <- LPSF1(TempMean = 15)
z4 <- LMA1()
resultsMatrix <- cbind(z4[2,4])
RegPlotF()
#resultsMatrix[1,] <- 
```
* Changing the population mean
```{r}
Exp1 <- LPSF1(PopsMean = 25)
z5 <- LMA1()
resultsMatrix <- cbind(z5[2,4])
RegPlotF()

```
* Changing the sample size
```{r}
Exp1 <- LPSF1(n = 15)
z6 <- LMA1()
resultsMatrix <- cbind(z6[2,4])
RegPlotF()

```

* Changing the sample size again, controlling all parameters
```{r}
Exp1 <- LPSF1(TempMean = 15, PopsMean = 15, sd1 = 1, sd2=1, n = 1500)
z7 <- LMA1(Exp1)
resultsMatrix <- cbind(z7[2,4])
RegPlotF()

print(resultsMatrix)
```
None of these experiments have consistant p-values due to the randomness generated using the rnorm function in the original data simulation script.




###Take 2###
Generating the data differently
```{r} 
#LPSF= Leucopis Population Simulation Function
#Produces a table of rnorm Temperatures and Populations
#Runs a linear model
#Creates a ggplot with a smoother
#Returns the data, slope, and p-values
LPSF2 <-function(n=50){
  x=rnorm(n,mean = 18, sd=2)
  noise <- runif(n,-20,20)
  y=5*x+noise
  Exp2 <- data.frame(x,y)
  myMod <- lm(y~x) #fits model
  myOut <- c(slope=summary(myMod)$coefficients[2,1],pval=summary(myMod)$coefficients[2,4])
  plotVar <- ggplot(data = Exp2, aes(x=x,y=y))+ geom_point()+ stat_smooth(method = lm, se=0.99)
  print(plotVar)
  return(myOut)

}
LPSF2()
LPSF2(200)
LPSF2(10)
LPSF2(5)
```

Now I can have a pretty small n and still have a good p value since the model is pretty tight and the noise isn't very strong.
x in this scenario is temperature and y is population